Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-09-22 paper/problem_description.tex
Updated BibTeX use and the Makefile

\begin{tabular}{ p{4cm} p{11cm}}
Deadline: & 2010-12-20 \\
Submission date: & 2010-12-xx \\
Department: & Department of Telematics \\
Supervisor: & Danilo Gligoroski \\\\
\end{tabular}
\vspace{0.5cm}

>>>>

\begin{tabular}{ p{4cm} p{11cm}}
Deadline: & 2010-12-20 \\
Department: & Department of Telematics \\
Supervisor: & Danilo Gligoroski \\\\
\end{tabular}
\vspace{0.5cm}
